Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-28 doc/main_jfm.tex
working on shear example

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Shear Flow}
\label{sec:ves_in_shear}
To study the deformation of a Janus-vesicle under a shear flow using the proposed algorithm, 
we adopt a widely tested numerical simulation in both continuum and molecular dynamics models, single vesicle under a shear flow. 
The background flow is a shear flow 
\begin{equation}
\uu_{\infty}(\xx) = \dot\gamma  \xx \cdot \mathbf{e}_2 \mathbf{e}_1
\end{equation}
with shear rate $\dot\gamma$
and orthogonal unit vectors $\mathbf{e}_x$ and $\mathbf{e}_y$ for the horizontal and vertical directions respectively. 
The well known results indicate that the vesicle has tank-treading behavior when 
there is no viscosity contrast in both fluids inside and outside of the vesicle. Within the framework of the simulation setup, the proposed model provides a feature that the fluid viscosity is constant over the computational domain and it is capable of performing these simulations.

The centroid of the pre-relaxed $58$-body Janus vesicle is initially placed at the origin then the shear flow 
with a certain shear rate $\chi$ is then turned on. 
The snapshots of the simulation for single vesicle in a shear flow with a shear rate $\chi=0.0025$ are shown 
in Figure~\ref{figure3}.
Panels (a)-(b) show the initial shape obtained from the relaxation run and the deformed 
configuration of the Janus-vesicle after a period of time ($t=4000$) is in panels (c)-(d). 
The background color in panels (a) and (c) presented in the figure is the strength of the action due to the
hydrophobic attraction. From weak to strong action field, the color varies from blue to red. Clearly, the
hydrophobic layer has the largest action. To demonstrate the tank-treading behavior of the vesicle, panels (b) 
and (d) provide the streamlines of the fluid velocity over the whole computational domain when the shear 
flow passes through the structure. The tank-treading motion of the structure is then observed, for instance,
the particle velocities in panel (d) indicate a clockwise tank-treading movement.

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{N58_0.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
  \caption{Vesicle under a shear flow where the shear rate $\chi=0.0025$: 
  (a) Initial configuration of 58-body Janus-vesicle where black arrows are the particle orientations; 
  (b) The fluid velocity plot with respect to the configuration in (a); Streamlines are plotted in the background
  as solid curves. Red arrows represent the particle velocities.
  (c) Deformed vesicle after $20000$ steps. The tank-treading motion occurs after reaching the state shown in panel (c).
  (d) The fluid velocity plot with respect to the configuration in (c);
  The background colors in panels (a) and (c) represent the strength of the hydrophobic attraction potential. The blue region shows no action and the red region in the bilayer gives the strongest action.
  }
    \label{figure3}
\end{figure}
%
%

In order to extract more physical properties of the proposed model, we track the total length of the bilayer structure, the reduced area over the time, and the excess length. Here the enclosed area and the total length of the structure are calculated from the midplane.
These results are shown in Figure~\ref{figure4} where we compare results from the use of a set of shear 
rates $\chi=\{0.002,0.0025,0.003,0.0035\}$. 
The reduced area is given by $A^* = 4\pi A/L^2$ where $A$ the area, and $L$ the total length of the Janus-vesicle with respect to the midplane. 
Furthermore, the excess length is given by $\Delta=L/\sqrt{A^*/\pi}-2\pi$.
Since the starting configuration is close to a circular shape, the reduced area decreases from a value very close to $1$. For the test cases in Figure~\ref{figure4}, the smooth curves in panel (a) are fitted using an
exponential model given by $A^* = a_0 + b_0 \exp(-kt)$. Panel (b) shows that the decay rate $k$ is independent of the shear rate when the shear is above a threshold and the terminal reduced areas for each 
case of the shear rates are given in the inset. It is also clear that a slower shear rate generates a higher terminal reduced area and has a faster convergence then the high shear rate cases. 
With a converging total arc length as shown in panel (c), a slower shear rate also produces a smaller excess length shown in panel (d).
In summary, the small oscillations in all results are due to the granularity of the Janus-vesicle which tend to having slightly non-smooth curves in simulations. Overall the total lengths of the bilayer have the same converging value in all test shear rates. Moreover, based on the numerical experiments, we observe that the reduce area converges relatively early when the shear rate is lower than $\chi=0.003$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Shear Flow}
\label{sec:ves_in_shear}
We begin by studying the dynamics of a single Janus-vesicle suspended in
the shear flow
\begin{align}
  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_2) \mathbf{e}_1,
\end{align}
with shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_1$
and $\mathbf{e}_2$ for the horizontal and vertical directions
respectively. It is well known that a vesicle has tank-treading behavior
when there is no viscosity contrast between the fluids inside and
outside of the vesicle.
%Within the framework of the simulation setup,
%the proposed model provides a feature that the fluid viscosity is
%constant over the computational domain and it is capable of performing
%these simulations.

The centroid of the pre-relaxed $58$-body Janus vesicle is initially
placed at the origin and the shear flow with a certain shear rate $\chi$
is applied. Snapshots of the Janus-vesicle in a shear flow with a shear
rate $\chi=0.0025$ are shown in Figure~\ref{figure3}. Panels (a) and (b)
show the initial shape obtained from the relaxation run and the deformed
configurations of the Janus-vesicle at time $t=4000$ are in panels (c)
and (d). The background color in panels (a) and (c) is the strength of
the action of the hydrophobic attraction. Red corresponds to a strong
action while blue is weak action. The hydrophobic layer clearly has the
strongest action. To demonstrate the tank-treading behavior of the
vesicle, panels (b) and (d) provide the streamlines of the fluid
velocity around the Janus-vesicle. In panel (d), we can clearly observe
the clockwise tank-treading motion.

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{N58_0.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
  \caption{\label{figure3} A Janus-vesicle suspended in a shear flow
  with shear rate $\chi=0.0025$: (a) Initial configuration of 58-body
  Janus-vesicle where black arrows are the particle orientations. (b)
  The particle velocities and streamlines of the configuration in (a).
  Streamlines are plotted in the background as solid curves. Red arrows
  represent the particle velocities. (c) Deformed Janus-vesicle at
  $t=4000$. At this configuration the Janus-vesicle is tank-treading.
  (d) The particle velocities and streamlines of the configuration in
  (c). The background colors in panels (a) and (c) represent the
  strength of the hydrophobic attraction potential. The blue region
  shows no action and the red region in the bilayer gives the strongest
  action.}
\end{figure}
%
%
\todo[inline]{Bryan left off here}
In order to extract more physical properties of the proposed model, we
track the total length of the bilayer structure, the reduced area over
the time, and the excess length. Here the enclosed area and the total
length of the structure are calculated from the midplane.  These results
are shown in Figure~\ref{figure4} where we compare results from the use
of a set of shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$.  The
reduced area is given by $A^* = 4\pi A/L^2$ where $A$ the area, and $L$
the total length of the Janus-vesicle with respect to the midplane.
Furthermore, the excess length is given by
$\Delta=L/\sqrt{A^*/\pi}-2\pi$.  Since the starting configuration is
close to a circular shape, the reduced area decreases from a value very
close to $1$. For the test cases in Figure~\ref{figure4}, the smooth
curves in panel (a) are fitted using an exponential model given by $A^*
= a_0 + b_0 \exp(-kt)$. Panel (b) shows that the decay rate $k$ is
independent of the shear rate when the shear is above a threshold and
the terminal reduced areas for each case of the shear rates are given in
the inset. It is also clear that a slower shear rate generates a higher
terminal reduced area and has a faster convergence then the high shear
rate cases.  With a converging total arc length as shown in panel (c), a
slower shear rate also produces a smaller excess length shown in panel
(d).  In summary, the small oscillations in all results are due to the
granularity of the Janus-vesicle which tend to having slightly
non-smooth curves in simulations. Overall the total lengths of the
bilayer have the same converging value in all test shear rates.
Moreover, based on the numerical experiments, we observe that the reduce
area converges relatively early when the shear rate is lower than
$\chi=0.003$.
